Backpropagating Gravitational wave events

### 2022-05-07 src/ms.tex
Will starts to work on intro.

\section{Introduction}
As the detection rate of gravitation waves (GWs) from merging double-compact-object (DCO) binaries increases 
with the sensitivity of the ground-based GW detector network \citep{Abbott2018,LIGOScientificCollaboration2015,Buikema2020,Tse2019,Acernese2015,Acernese2019,Aso2013,Akutsu2021}, the ability to disentangle the astrophysical processes 
which shape the evolution of GW progenitor populations is becoming increasingly attainable. One of the most common ways
to study progenitor populations of GW mergers is through population synthesis simulations for a host of formation environments
including isolated binary stars, triple systems, globular clusters, nuclear star clusters, AGN disks, and more 
cite Mandel \& Broekgaarden. In these types of studies, the population is forward modeled based on random samples from
empirically or theoretically motivated distributions of initial parameters which define the age, metallicity, and intrinsic 
properties of the population like masses, orbital separations, and eccentricities. These initial populations are then evolved
using a set of assumptions for how astrophysical processes impact the evolution of the DCO merger progenitors, ultimately producing
a synthetic catalog of mergers which can be compared of observations from ground-based GW detectors.

>>>>

\section{Introduction}
As the detection rate of gravitation waves (GWs) from merging
double-compact-object (DCO) binaries increases with the sensitivity of the
ground-based GW detector network
\citep{Abbott2018,LIGOScientificCollaboration2015,Buikema2020,Tse2019,Acernese2015,Acernese2019,Aso2013,Akutsu2021},
we are beginning to constrain the astrophysical processes which shape the
evolution of GW progenitor populations. One of the most common ways to study
progenitor populations of GW mergers is through population synthesis simulations
for a host of formation environments including isolated binary stars, triple
systems, globular clusters, nuclear star clusters, AGN disks, and more
\citep{Mandel2022}. \wf{Moar citations here} In these types of studies, the
population is forward modeled based on random samples from empirically or
theoretically motivated distributions of initial parameters which define the
age, metallicity, and intrinsic properties of the population like masses,
orbital separations, and eccentricities. These initial populations are then
evolved using a set of assumptions for how astrophysical processes impact the
evolution of the DCO merger progenitors, ultimately producing a synthetic
catalog of mergers which can be compared of observations from ground-based GW
detectors.
